### 2018-07-08 article.tex
Scheme.

\title
[Short Title]
{
	The undersampling ensemble approach to highly imbalanced data classification%\titlebreak
}

@@

This is a sample article that uses the \textsf{jmlr} class with
the \texttt{wcp} class option.  Please follow the guidelines in
this sample document as it can help to reduce complications when
combining the articles into a book. Please avoid using obsolete
commands, such as \verb|\rm|, and obsolete packages, such as
\textsf{epsfig}.\footnote{See
\url{http://www.ctan.org/pkg/l2tabu}}

Please also ensure that your document will compile with PDF\LaTeX.
If you have an error message that's puzzling you, first check for it
at the UK TUG FAQ
\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=man-latex}.  If
that doesn't help, create a minimal working example (see
\url{http://theoval.cmp.uea.ac.uk/~nlct/latex/minexample/}) and post
to somewhere like TeX on StackExchange
(\url{http://tex.stackexchange.com/}) or the LaTeX Community Forum
(\url{http://www.latex-community.org/forum/}).

\begin{note}
This is an numbered theorem-like environment that was defined in
this document's preamble.
\end{note}

\subsection{Sub-sections}

Sub-sections are produced using \verb|\subsection|.

\subsubsection{Sub-sub-sections}

Sub-sub-sections are produced using \verb|\subsubsection|.

\paragraph{Sub-sub-sub-sections}

Sub-sub-sub-sections are produced using \verb|\paragraph|.
These are unnumbered with a running head.

\subparagraph{Sub-sub-sub-sub-sections}

Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
These are unnumbered with a running head.

\section{Cross-Referencing}

Always use \verb|\label| and \verb|\ref| (or one of the commands
described below) when cross-referencing.  For example, the next
section is Section~\ref{sec:math}. The \textsf{jmlr} class
provides some convenient cross-referencing commands:
\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
\verb|\exampleref| and \verb|\appendixref|. The argument of these
commands may either be a single label or a comma-separated list
of labels. Examples:

Referencing sections: \sectionref{sec:math} or
\sectionref{sec:intro,sec:math} or
\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.

Referencing equations: \equationref{eq:trigrule} or
\equationref{eq:trigrule,eq:df} or
\equationref{eq:trigrule,eq:f,eq:df,eq:y}.

Referencing tables: \tableref{tab:operatornames} or
\tableref{tab:operatornames,tab:example} or
\tableref{tab:operatornames,tab:example,tab:example-booktabs}.

Referencing figures: \figureref{fig:nodes} or
\figureref{fig:nodes,fig:teximage} or
\figureref{fig:nodes,fig:teximage,fig:subfigex} or
\figureref{fig:circle,fig:square}.

Referencing algorithms: \algorithmref{alg:gauss} or
\algorithmref{alg:gauss,alg:moore} or
\algorithmref{alg:gauss,alg:moore,alg:net}.

Referencing theorem-like environments: \theoremref{thm:eigenpow},
\lemmaref{lem:sample}, \remarkref{rem:sample}, 
\corollaryref{cor:sample}, \definitionref{def:sample},
\conjectureref{con:sample}, \axiomref{ax:sample} and
\exampleref{ex:sample}.

Referencing appendices: \appendixref{apd:first} or
\appendixref{apd:first,apd:second}.

\section{Equations}
\label{sec:math}

The \textsf{jmlr} class loads the \textsf{amsmath} package, so
you can use any of the commands and environments defined there.
(See the \textsf{amsmath} documentation for further
details.\footnote{Either \texttt{texdoc amsmath} or
\url{http://www.ctan.org/pkg/amsmath}})

Unnumbered single-lined equations should be displayed using
\verb|\[| and \verb|\]|. For example:
\[E = m c^2\]
Numbered single-line equations should be displayed using the
\texttt{equation} environment. For example:
\begin{equation}\label{eq:trigrule}
\cos^2\theta + \sin^2\theta \equiv 1
\end{equation}
This can be referenced using \verb|\label| and \verb|\equationref|.
For example, \equationref{eq:trigrule}.

Multi-lined numbered equations should be displayed using the
\texttt{align} environment.\footnote{For reasons why you 
shouldn't use the obsolete \texttt{eqnarray} environment, see
Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
\begin{align}
f(x) &= x^2 + x\label{eq:f}\\
f'(x) &= 2x + 1\label{eq:df}
\end{align}
Unnumbered multi-lined equations should be displayed using the
\texttt{align*} environment. For example:
\begin{align*}
f(x) &= (x+1)(x-1)\\
&= x^2 - 1
\end{align*}
If you want to mix numbered with unnumbered lines use the
align environment and suppress unwanted line numbers with
\verb|\nonumber|. For example:
\begin{align}
y &= x^2 + 3x - 2x + 1\nonumber\\
&= x^2 + x + 1\label{eq:y}
\end{align}
An equation that is too long to fit on a single line can be
displayed using the \texttt{split} environment. 
Text can be embedded in an equation using \verb|\text| or
\verb|\intertext| (as used in \theoremref{thm:eigenpow}).
See the \textsf{amsmath} documentation for further details.

\subsection{Operator Names}
\label{sec:op}

Predefined operator names are listed in \tableref{tab:operatornames}.
For additional operators, either use \verb|\operatorname|,
for example $\operatorname{var}(X)$ or declare it with
\verb|\DeclareMathOperator|, for example
\begin{verbatim}
\DeclareMathOperator{\var}{var}
\end{verbatim}
and then use this new command. If you want limits that go above and
below the operator (like \verb|\sum|) use the starred versions
(\verb|\operatorname*| or \verb|\DeclareMathOperator*|).

\begin{table}[htbp]
\floatconts
  {tab:operatornames}%
  {\caption{Predefined Operator Names (taken from 
   \textsf{amsmath} documentation)}}%
  {%
\begin{tabular}{rlrlrlrl}
\cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
\cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
\cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
\cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
\cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
\cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
\cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
\cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
\cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
\end{tabular}\par
\begin{tabular}{rlrl}
\cs{varlimsup} & $\varlimsup$ 
& \cs{varinjlim} & $\varinjlim$\\
\cs{varliminf} & $\varliminf$ 
& \cs{varprojlim} & $\varprojlim$
\end{tabular}
}
\end{table}

\section{Vectors and Sets}
\label{sec:vec}

Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
The \textsf{jmlr} class also provides \cs{set} to typeset a
set. For example $\set{S}$.

\section{Floats}
\label{sec:floats}

Floats, such as figures, tables and algorithms, are moving
objects and are supposed to float to the nearest convenient
location. Please don't force them to go in a particular place. In
general it's best to use the \texttt{htbp} specifier and don't
put the figure or table in the middle of a paragraph (that is
make sure there's a paragraph break above and below the float).
Floats are supposed to have a little extra space above and below
them to make them stand out from the rest of the text. This extra
spacing is put in automatically and shouldn't need modifying.

To ensure consistency, please \emph{don't} try changing the format of the caption by doing
something like:
\begin{verbatim}
\caption{\textit{A Sample Caption.}}
\end{verbatim}
or
\begin{verbatim}
\caption{\em A Sample Caption.}
\end{verbatim}
You can, of course, change the font for individual words or 
phrases, for example:
\begin{verbatim}
\caption{A Sample Caption With Some \emph{Emphasized Words}.}
\end{verbatim}

\subsection{Tables}
\label{sec:tables}

Tables should go in the \texttt{table} environment. Within this
environment use \verb|\floatconts| (defined by \textsf{jmlr})
to set the caption correctly and center the table contents.

\begin{table}[htbp]
 % The first argument is the label.
 % The caption goes in the second argument, and the table contents
 % go in the third argument.
\floatconts
  {tab:example}%
  {\caption{An Example Table}}%
  {\begin{tabular}{ll}
  \bfseries Dataset & \bfseries Result\\
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876
  \end{tabular}}
\end{table}

If you want horizontal rules you can use the \textsf{booktabs}
package which provides the commands \verb|\toprule|, 
\verb|\midrule| and \verb|\bottomrule|. For example, see
\tableref{tab:example-booktabs}.

\begin{table}[hbtp]
\floatconts
  {tab:example-booktabs}
  {\caption{A Table With Horizontal Lines}}
  {\begin{tabular}{ll}
  \toprule
  \bfseries Dataset & \bfseries Result\\
  \midrule
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876\\
  \bottomrule
  \end{tabular}}
\end{table}

If you want vertical lines as well, you can't use the
\textsf{booktabs} commands as there'll be some unwanted gaps.
Instead you can use \LaTeX's \verb|\hline|, but the rows may
appear a bit cramped.  You can add extra space above or below a
row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
see \tableref{tab:example-hline}.

\begin{table}[htbp]
\floatconts
  {tab:example-hline}
  {\caption{A Table With Horizontal and Vertical Lines}}%
  {%
    \begin{tabular}{|l|l|}
    \hline
    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
    \abovestrut{2.2ex}Data1 & 0.12345\\
    Data2 & 0.67890\\
    Data3 & 0.54321\\
    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
    \end{tabular}
  }
\end{table}

If you want to align numbers on their decimal point, you can
use the \textsf{siunitx} package. For example, see
\tableref{tab:example-siunitx}. For further details see the
\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.

\begin{table}[htbp]
\floatconts
  {tab:example-siunitx}
  {\caption{A Table With Numbers Aligned on the Decimal Point}}
  {\begin{tabular}{lS[tabformat=3.5]}
  \bfseries Dataset & {\bfseries Result}\\
  Data1 & 0.12345\\
  Data2 & 10.6789\\
  Data3 & 50.543\\
  Data4 & 200.09876
  \end{tabular}}
\end{table}

If the table is too wide, you can adjust the inter-column
spacing by changing the value of \verb|\tabcolsep|. For
example:
\begin{verbatim}
\setlength{\tabcolsep}{3pt}
\end{verbatim}
If the table is very wide but not very long, you can use the
\texttt{sidewaystable} environment defined in the
\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
If the table is too long to fit on a page, you should use the
\texttt{longtable} environment defined in the \textsf{longtable}
package (so use \verb|\usepackage{longtable}|).

\subsection{Figures}
\label{sec:figures}

Figures should go in the \texttt{figure} environment. Within this
environment, use \verb|\floatconts| to correctly position the
caption and center the image. Use \verb|\includegraphics|
for external graphics files but omit the file extension. Do not
use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
image, it's better to use a fraction of the line width rather
than an explicit length. For example, see \figureref{fig:nodes}.

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:nodes}
  {\caption{Example Image}}
  {\includegraphics[width=0.5\linewidth]{images/nodes}}
\end{figure}

If your image is made up of \LaTeX\ code (for example, commands
provided by the \textsf{pgf} package) you can include it using
\cs{includeteximage} (defined by the \textsf{jmlr} class). This
can be scaled and rotated in the same way as \cs{includegraphics}.
For example, see \figureref{fig:teximage}.

\begin{figure}[htbp]
\floatconts
  {fig:teximage}
  {\caption{Image Created Using \LaTeX\ Code}}
  {\includeteximage[angle=45]{images/teximage}}
\end{figure}

If the figure is too wide to fit on the page, you can use the
\texttt{sidewaysfigure} environment defined in the
\textsf{rotating} package.

Don't use \verb|\graphicspath|. If the images are contained in
a subdirectory, specify this when you include the image, for
example \verb|\includegraphics{figures/mypic}|.

\subsubsection{Sub-Figures}
\label{sec:subfigures}

\begin{sidewaystable}
\scriptsize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.15}
\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%

\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}

\\
\multicolumn{10}{|c||}{}&
\multicolumn{10}{c||}{}&
\multicolumn{3}{c|}{}&

	 \\

	\multicolumn{5}{|c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} &
	\multicolumn{5}{c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} 
	& & & & \\

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}

	& & & &

	\\

	&&&&&&&&&&&&&&&&&&&&&&&
	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/GNB.csv}{}%
	{

	\ereg & \ewei & \ecwei & \enwei & \encwei &
	\eregr & \eweir & \ecweir & \enweir & \encweir &
	\eregos & \eweios & \ecweios & \enweios & \encweios & 
	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
	\os & \us & \reg &

	\multicolumn{1}{l|}{\emph{\dataset}}

	}%
\end{tabular}
\caption{Balanced accuracy scores obtained using \textsc{gnb} as a base classifier}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.15}
\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%

\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}

\\
\multicolumn{10}{|c||}{}&
\multicolumn{10}{c||}{}&
\multicolumn{3}{c|}{}&

	 \\

	\multicolumn{5}{|c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} &
	\multicolumn{5}{c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} 
	& & & & \\

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}

	& & & &

	\\

	&&&&&&&&&&&&&&&&&&&&&&&
	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/kNN.csv}{}%
	{

	\ereg & \ewei & \ecwei & \enwei & \encwei &
	\eregr & \eweir & \ecweir & \enweir & \encweir &
	\eregos & \eweios & \ecweios & \enweios & \encweios & 
	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
	\os & \us & \reg &

	\multicolumn{1}{l|}{\emph{\dataset}}

	}%
\end{tabular}
\caption{Balanced accuracy scores obtained using \textsc{knn} as a base classifier}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.15}
\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%

\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}

\\
\multicolumn{10}{|c||}{}&
\multicolumn{10}{c||}{}&
\multicolumn{3}{c|}{}&

	 \\

>>>>

\title
[Fusers in homogenous ensemble of undersampled majority class]
{
	Fusers in homogenous ensemble of undersampled majority class for highly imbalanced data classification%\titlebreak
}

@@

Additionally, in incremental learning, if the majority-class objects outnumber greatly the minority class, the latter can be completely ignored \cite{He:2009}. The aforementioned issues are reasons why most existing classification methods for imbalanced data are restricted to the \textit{offline} learning only, i.e., a case where the entire data set is provided prior to the analysis.

Most of the classification algorithms assume that there are no significant disproportions among instances from different classes. Nevertheless, in many practical tasks, we may observe that instances from one class (so-called \textit{majority class}) significantly outnumber the objects from remaining classes (\textit{minority class}). Most of traditional classifiers have a bias in favor of the majority class although more often the minority class is more interesting, because misidentification of an instance belonging to it is usually much more expensive than assigning an instance from majority class to minority one. A good example is an undetected fraud that would be more expensive than the cost of additional analysis of a correct transaction classified as fraudless transaction. Such a problem is known as imbalanced data classification \cite{Sun:2009,Wang:2017}, where an unequal number of instances from the examined classes plays a key role during the classifier learning. Various approaches have been proposed in the literature to tackle this challenging difficulty embedded in the nature of data. Usually, the researchers are focusing on maximizing the correct minority class classification. At the same time, performance on the majority class cannot be neglected.

\begin{figure}[!h]
\floatconts
  {fig:east}
  {\caption{Easy separable imbalance dataset}}
  {\includegraphics[clip=true, trim = 11 11 11 11, width=0.25\linewidth]{figures/easy}}
\end{figure}

In this project we will focus on binary imbalanced problems, because this setup is the one most frequently studied in the literature and most commonly meet in practical problems, e.g.,\textit{fault detection} or \textit{spam filtering}. Therefore, another important issue is proposing an appropriate quality measure that would be adequate for imbalanced data classification \cite{Elazmeh:2006}.

In case of imbalanced data classification the disproportion between the different classes is not the sole issue of learning difficulties. One may easily came up with an example where the instance distributions from different classes are well-separated, as depicted in Fig.\ref{fig:easy}.

Proposing a efficient classifier for such a task is not a challenge. Unfortunately, instances from the minority class often form clusters of an unknown structure that are scattered \cite{Napierala:2012}. Additional complication comes from the fact that during learning, the number of intactness from the minority class may be not sufficient enough for the learning algorithm to acquire the appropriate generalization level, which in effect can cause \emph{overfitting} \cite{Chen:2008}. All those problems are a focus of intense research \cite{Chawla:2002,Bunkhumpornpat:2009,Kubat:1997}.

Methods for imbalanced data classification can be divided into three main groups \cite{Lopez:2012}.

\begin{figure}[!h]
\floatconts
  {fig:subfigex}
  {\caption{Examples of data preprocessing methods.}}
  {%
    \subfigure[Original dataset]{\label{fig:circle}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 11 141 141 11]
    {figures/preprocessing}}%
    \qquad
    \subfigure[\textsc{smote}]{\label{fig:circle}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 141 141 11 11]
    {figures/preprocessing}}%

    \subfigure[\textsc{adasyn}]{\label{fig:circle}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 11 11 141 141]
    {figures/preprocessing}}%
    \qquad
    \subfigure[Undersampling]{\label{fig:circle}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 141 11 11 141]
    {figures/preprocessing}}%
  }
\end{figure}

\noindent\textbf{ Data preprocessing methods}. This approach focuses on reducing the number of objects in majority class (\emph{undersampling}) or generating new objects of the minority class (\textit{oversampling}). The difference between \emph{under-} and \emph{oversampling} is presented in Fig. \ref{fig:over-under}.

These mechanisms have the objective of balancing the quantity of instances from considered classes. For oversampling, new instances are random copies of existing ones or are generated in a guided manner. The most popular method is \textsc{smote} \cite{Cha2002} algorithm, which creates new instances on a basis of existing ones by slightly modifying the values of their attributes. As a result, new artificial examples that are in compliance with the minority class distribution are generated.  Other oversampling methods are \textsc{adasyn} \cite{He:2008}, in which a difficulty of an object for the classifying model is considered or \textsc{ramob}oost \cite{Chen:2010}. Unfortunately, methods such as \textsc{smote} may lead to changes in the characteristic of the minority class and in result to \emph{overfitting} the classifier, what was shown in Fig. \ref{fig:wrong_smote}.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex}
  {\caption{Example of wrong \textsc{smote} oversampling.}}
  {%
    \subfigure[Original dataset]{\label{fig:circle}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 11 11 141 11]
    {figures/wrong_smote}}%
    \qquad
    \subfigure[\textsc{smote}]{\label{fig:circle}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 141 11 11 11]
    {figures/wrong_smote}}%
  }
\end{figure}

W WYPADKU UNDERSAMPLINGU NIE WYSTEPUJE RYZYKO NIESŁUSZNEGO ROZSZERZENIA PRZESTRZENI WZORCÓW KLASY MNIEJSZOŚCIOWEJ, CO MA MIEJSCE W CHOĆBY SMOTE.

Several modifications of \textsc{smote} have been proposed that are able to identify the instances to be copied in a more intelligent fashion such as \emph{Borderline}\textsc{smote} \cite{Han:2005}. It generates new instances from the minority class close to the decision border. \emph{Safe-Level} \textsc{smote} \citep{Bunkhumpornpat:2009} and \textsc{ln}-\textsc{smote} \cite{Maciejewski:2011} reduce the probability of generating synthetic instances of the minority class in areas where the predominant objects are that of the majority class. It is worth noticing that our team proposed two novel solutions to this problem: \textsc{rbo} \cite{koziarski2017radial} and \textsc{ccr} that enforce instances from the majority-class to be relocated from the areas where the minority-class instances are present \cite{Koziarski:2017amcs}. Methods of \emph{undersampling} are built around the idea of randomly removing the instances from the majority-class or removing them from the areas in such way that the  quality of the classifier is not disrupted using neighbor analysis.%\todo{W opisie metod przetwarzania wstępnego skupiamy się chyba wyłącznie na \emph{oversamplingu}.}\todo{Nie uwzględniłem czystego losowego \emph{oversamplingu}, bo skoro powtarza istniejące już obiekty, to ilustracja byłaby bezsensowna.}

%\begin{figure}[hbt]
%\centering
%\includegraphics[width=.9\linewidth]{figures/smote}
%\caption{Example of oversampling using \textsc{smote}}
%\end{figure}

\noindent\textbf{ Inbuilt mechanisms.} In this approach existing classification algorithms are adapted for imbalanced problems ensuring balanced accuracy for instances from both classes. Two of the most popular areas of research of this methods are using one-class classification  \cite{Japkowicz:1995}, usually known as learning without counterexamples, where the goal is to learn the minority class decision areas and because of the frequently assumed regular, closed shape of the decision borders is adequate to the clusters created by minority classes \cite{Krawczyk:2014ins}. The disproportion between the number of instances in classes is then omitted. Another approach is the (\textit{cost sensitive}) classification, where the algorithm takes into account the asymmetrical loss function that assigns a higher cost to a misclassification of an instance form a minority class \cite{Krawczyk:2014,Lopez:2012,He:2009,Zhou:2006}. Unfortunately such methods can cause a reverse bias towards the minority class. 
Worth noting are methods based on ensemble classification \cite{Wozniak:2014}, like \emph{\textsc{smote}Boost} \cite{Chawla:2003} and \emph{AdaBoost.NC} \cite{Wang:2010}%, or \emph{Multi-objective Genetic Programing Ensemble} \cite{Bhowan:2013}.

\noindent\textbf{Hybrid methods.} They combine the advantages of methods using data pre-processing with the classification methods. The most popular category is the hybridisation of \emph{under-} and \emph{oversampling} with ensemble classifiers \cite{Galar:2012}. This approach allows the data to be independently  processed for each of the base model. Algorithms formed on modifications of \emph{Bagging} and \emph{Boosting} \cite{Chawla:2003} enjoy wide popularity.

The main contributions of this work are:

%%%
%%% Introduction
%%%
\section{Homogenous ensemble based on undersampling the majority class}
\label{sec:intro}

Zaawansowane metody oversamplingu nie są możliwe do zastosowania przy sytuacji, gdzie w zbiorze uczącym znajduje się zaledwie kilka wzorców.

Idea k-foldowego podziału klasy większościowej. Wyznaczanie wartości k jako zaokrąglonego IR. Atut w postaci wykorzystania wszystkich wzorców, gdzie tworzymy komitet k zbalansowanych zbiorów.

\begin{figure}[htbp]
\floatconts
  {fig:teximage}
  {\caption{Scheme of using k-Fold division in ensemble construction}}
  {\includeteximage[angle=0]{figures/ensemble_scheme}}
\end{figure}

Wyliczanie wag. Accuracy się nie sprawdzi, więc BAC.

Jeśli klasyfikujemy nie jeden wzorzec, a wiele, wagi mogą być też dla pojedynczych próbek, dla podbicia, a więc pojawia się KONTRAST. Mamy takie ładne ilustracje z badań, dodajmy rysunek chociaż jeden poglądowo.

\begin{figure}[!h]
\floatconts
  {fig:subfigex}
  {\caption{Rysunek.}}
  {%
    \subfigure[O jaki ładny]{\label{fig:circle}%
    \includegraphics[width=.5\linewidth, trim = 0 100 0 100,clip=true]
    {figures/ecoli-0-1_vs_2-3-5}}%
    \subfigure[A ten brzydki]{\label{fig:circle}%
    \includegraphics[width=.5\linewidth, trim = 0 100 0 100,clip=true]
    {figures/ecoli-0-3-4-6_vs_5}}%
  }
\end{figure}

Potencjał kontrastu dla danych strumieniowych.

Proponowane metody decyzyjne.

\begin{itemize}
	\item - akumulacja wsparć,
	\item - akumulacja ważona po członkach komitetu, gdzie waga to BAC dla zbioru uczącego,
	\item - akumulacja ważona po wzorcach, przez kontrast,
	\item - akumulacja znormalizowanych wag członków,
	\item - iloczyn znormalizowanych wag i kontrastu
\end{itemize}

Duża skala niezbalansowania to duża wielkość komitetu (ilustracja zależności na wykresie). Przyda się więc przycinanie (pruning).

Wyjaśnienie podejścia do pruningu. Wyliczamy wzajemną zależność statystyczną (Wilcoxonem) pomiędzy wsparciami członków i grupujemy -- omijając kwestię 1z2 2z3 ale nie 1z3 -- je uśredniając wsparcia w obrębie grupy. Uśredniamy też wagi i tworzymy tak dwupoziomowy system fuzji (potrzebna ilustracja).

Pruning też jest w kontekście klasyfikacji wielu wzorców na raz.

Wyjaśnienie kwestii wspomnianej wcześniej i uzasadnienie pominięcia jej analizy.

%%%
%%% Introduction
%%%
\section{Experiment design}
\label{sec:intro}

Wybrane zbiory danych.

Wykorzystane klasyfikatory bazowe. Wyjaśnienie dlaczego odrzuciliśmy MLP (brak konwergencji na bardzo niewielkich zbiorach) i SVC (nie jest on naturalnie probabilistyczny, a jego probabilistyczna interpretacja jest silnie zakłamana przy niewielkich zbiorach danych). Stąd bierzemy GNB, kNN i DT, przy domyślnych parametrach z sklearn.

Powównawczo uczenie na pełnym zbiorze i zbiorach po pojedynczym under i oversamplingu.

Undersampling, ze względu na niestabilność, powtórzony pięciokrotnie na każdym foldzie.

Zastosowana metoda podziału -- wymuszone przez KEEL k-fold CV (z k=5).

Zastosowana miara jakości -- zbalansowana dokładność, wymierna w niezbalansowanych danych.

Zastosowana analiza statystyczna -- parowa zależność pomiędzy klasyfikatorem z najwyższym rezultatem a pozostałymi w postaci testu Wilcoxona.

Przygotowane oprogramowanie ze wskazaniem repozytorium.

%%%
%%% Introduction
%%%
\section{Experimental evaluation}
\label{sec:intro}

Przedstawienie tabel.

\begin{sidewaystable}
	\restable{GNB}{\textsc{gnb}}
\end{sidewaystable}

\begin{sidewaystable}
	\restable{kNN}{k\textsc{nn}}
\end{sidewaystable}

\begin{sidewaystable}
	\restable{DTC}{\textsc{dtc}}
\end{sidewaystable}

Tabela zbiorcza zwycięstw w zależności od parametrów (z grupowaniem).

Interpretacja wyników, czyli co zostało należycie uprawdopodobnione.

%%%
%%% Conclusions
%%%
\section{Conclusions}
\label{sec:intro}
Co zostało zaproponowane.

Na co pozwala taka metoda.

Do jakich rezultatów doprowadziła.

Jakie są plany na przyszłość (czyli co robisz w wakacje).

%%%
%%% Acknowledgements and references
%%%
\acks{
	Acknowledgements go here.
}
\bibliography{bibliography}
